---
title: "Multi-organ imaging clarifies the connected subclinical pathology of the heart-brain-liver axis in UK Biobank   | Enrich Data script"

author: "Celeste McCracken"
date:   "25 May 2022"
output: html_notebook
---


### Setup
```{r}
source("00_setup.R")

proc<- read_xlsx("../Proc.xlsx")
```


### Main data input
```{r}
IP<- readRDS("../Dev Data 1/IP_0.rds"); dim(IP); get_checksum(IP)
# [1] 502462    236
# [1] 97427.62

```

#---------------
### 0. Simple adjustments
```{r}


IP$obese<- ifelse(IP$bmi_2_imp >= 30, 1, 0); table(IP$obese)
#     0     1 
# 39879  9117 

IP$NAFLD<- ifelse(IP$pdff >= 5, 1, 0); table(IP$NAFLD)
#    0     1 
# 11864  3623

IP$age_sq<-    IP$age_2^2
IP$cf_age_sq<- IP$cf_age_2^2

## Binary form of site

HBL<- IP$cardiac_flag & IP$brain_imaging_flag & IP$liver_flag

table(HBL, IP$cf_UKB_site_name_2)
# HBL     Cheadle (imaging) Bristol (imaging) Newcastle (imaging) Reading (imaging)
#   FALSE             13714                 0                8018              5111
#   TRUE              11755                 0                2069                 0

IP$site<-  ifelse(IP$cf_UKB_site_name_2 %like% "Cheadle", 1, 0)
table(IP$site)


smoking<- readRDS("~/Documents/UKB Test Space/R/smoking.rds")

IP<- left_join(IP, smoking %>% select(f.eid, smoking_cat_2))
```


### 1. CMR Indexing and ratios

```{r}

# Indexed LVSV
IP$cmr_LVSV_i<-  IP$cmr_LVSV / IP$bsa_2_imp
plot(IP$cmr_LVSV, IP$cmr_LVSV_i)

### LV Mass-to-volume ratio
IP$cmr_LVM_LVEDV<- IP$cmr_LVM/IP$cmr_LVEDV
hist(IP$cmr_LVM_LVEDV)

## cmr_GFI
cavity_size<- (IP$cmr_LVEDV + IP$cmr_LVESV)/2
GV<-          with(IP, cavity_size + (cmr_LVM/1.05))

IP$cmr_GFI<- with(IP, cmr_LVSV/GV)
mean(IP$cmr_GFI, na.rm=TRUE) # 0.4756326

```


### 2. Average cognitive function

```{r}


cogfields<- c("cog_FI_2", "cog_prosMemory_2", "cog_RT_2", 
             "trans_cog_RT_2", 
             "cog_FI_2_imp", "cog_prosMemory_2_imp", "trans_cog_RT_2_imp", 
             "cog_FI_2_is_imp", "cog_prosMemory_2_is_imp", "trans_cog_RT_2_is_imp")

## Check that the negative ones have been reflected
plot(IP$cog_RT_2, IP$trans_cog_RT_2_imp)

cog_standard<-  c("cog_FI_2_imp", "cog_prosMemory_2_imp", "trans_cog_RT_2_imp")

cor(IP[, cog_standard], use= "pairwise.complete.obs")
#                      cog_FI_2_imp cog_prosMemory_2_imp trans_cog_RT_2_imp
# cog_FI_2_imp            1.0000000            0.2273477          0.1702348
# cog_prosMemory_2_imp    0.2273477            1.0000000          0.1175638
# trans_cog_RT_2_imp      0.1702348            0.1175638          1.0000000

X<- IP %>% filter(imaging== TRUE, cognition_flag== 1) %>% .[, c("f.eid", cog_standard)]

skim(X)
X[,-1]<- scale(X[,-1])

jb<- tibble(f.eid= X$f.eid, cog_standard_4= rowMeans(X[,-1]))

hist(jb$cog_standard_4); skim(jb$cog_standard_4)
#   skim_variable n_missing complete_rate      mean    sd    p0    p25    p50   p75  p100 hist 
# 1 data                  0             1 -1.57e-17 0.669 -3.02 -0.381 0.0786 0.459  5.19 ▁▇▅▁▁


IP<- left_join(IP, jb) 

```

### 4. Set Counts 1 
```{r}

table(IP$imaging)
#  FALSE   TRUE 
# 453462  48998 


table(IP$imaging, IP$Exclusion_criterion)

  #       0.Include 1.Missing critical covariates
  # FALSE    450460                          3028
  # TRUE      48999                             2

IP$remaining<- IP$imaging & IP$Exclusion_criterion %like% "0"

table(IP$remaining)
# FALSE   TRUE 
# 453466  48996
```


### 6. Set Counts 2 - Heart set and liver set
```{r}

table(IP$remaining)
# 48996

##  Heart  -------------------------------------------

temp<- IP[IP$remaining== TRUE, c("f.eid", "PDA_AoD", "cmr_LVSV_i", "cmr_LVM_LVEDV", "cmr_GFI")]

flag<- at_least_one_flag(temp)
table(flag)
# flag
# FALSE  TRUE 
# 16587 32409 

temp<- temp %>% filter(flag==TRUE) %>% select(f.eid) %>% mutate(heart_flag= 1)

IP<- IP %>% select(-any_of("heart_flag")) %>%
            left_join(temp) %>% 
             mutate(heart_flag= fixNAs(heart_flag)); sum(IP$heart_flag) #  32409

### Liver -------------------------------------------


temp<- IP[IP$remaining== TRUE, c("f.eid", "ct1", "pdff", "iron")]
mySkim(temp)
flag<- at_least_one_flag(temp)
table(flag)
# flag
# FALSE  TRUE 
# 33473 15523 

temp<- temp %>% filter(flag==TRUE) %>% select(f.eid) %>% mutate(liver_flag= 1)

IP<- IP %>% select(-any_of("liver_flag")) %>%
  left_join(temp) %>% mutate(liver_flag= fixNAs(liver_flag)); sum(IP$liver_flag) # 15523

# FALSE  TRUE 
# 33473 15523 
```

### 7. Set Counts 3 - HL and brain union sets
```{r}
### Union of brain imaging sets
IP$any_brain<- fixNAs(IP$brain_imaging_flag)
table(IP$remaining, IP$any_brain)
  #            0      1
  # FALSE 453465      1
  # TRUE    5460  43536

### Union of heart and liver
IP$liver_or_heart<- pmax(fixNAs(IP$liver_flag), fixNAs(IP$heart_flag))
table(IP$remaining, IP$liver_or_heart) # 32757

IP$liver_and_heart<- IP$liver_flag & IP$heart_flag
sum(IP$liver_and_heart) # 15175

table(IP$liver_and_heart, IP$liver_or_heart)

IP$intersection_set<- IP$remaining & ((IP$any_brain & IP$liver_or_heart) | IP$liver_and_heart )
table(IP$intersection_set)
#  FALSE   TRUE 
# 471054  31408 

```

### 8. Set Counts 4 - Non-missing covariates
```{r}

table(IP$intersection_set)
#  FALSE   TRUE 
# 471054  31408 

covs<- c("age_2", "sex",  "height_2_imp", "R01_Diabetes_status_2", "R02_High_cholesterol_status_2", "R03_Hypertension_status_2", 
         "smoker_2", "mets_2_imp", "alcohol_con_2_imp", "deprivation_Townsend_imp", "educ_imp", "sbp_2_imp", "obese",
         "bc_TchoL_0_imp", "bc_HbA1c_0_imp", "bc_RBC_0_imp")

IP$full_covariates<- apply(IP[,covs], 1, function(x) all(!is.na(x)))

table( IP$intersection_set, IP$full_covariates)
  #        FALSE   TRUE
  # FALSE 453732  17556
  # TRUE     730  30444



### There are 730 rows with missing biochemistry (2.3%)


IP$maximum_set<- IP$intersection_set & IP$full_covariates; table(IP$maximum_set)
#  FALSE   TRUE 
# 472018  30444

modvars<-   c( "cmr_LVSV_i", "cmr_LVM_LVEDV", "cmr_GFI", "PDA_AoD",
               "O_volume_grey_matter_2",   "O_volume_WMH_cbrt", "ICVF", "ISOVF",
               "ct1", "pdff") 

mid<- IP[IP$maximum_set, c("f.eid", modvars)]
N<- nrow(mid)

sk<- skim(mid) %>% mutate(non_missing_count= (N- n_missing)) %>% select(skim_variable, non_missing_count)

present<- apply(mid, 1, function(x) !any(is.na(x)))
table(present)
# FALSE  TRUE 
# 23579  6865 

SEM<- mid %>% filter(present)

## Liver subset

IP$liver_subset<- IP$maximum_set & IP$liver_flag
 
sum(IP$liver_subset) # 15097

# Checks
IP$full_covariates<- apply(IP[,covs], 1, function(x) all(!is.na(x)))
table(IP$liver_subset, IP$full_covariates)  
  #        FALSE   TRUE
  # FALSE 454462  32903
  # TRUE       0  15097


IP$SEM_flag<- ifelse(IP$f.eid %in% SEM$f.eid, 1, 0)
sum(IP$SEM_flag)

```


### 9. Check for skew
```{r}

myModelVars<- proc %>% filter(Check=="yes") %>% pull(Var) %>% print()

skewTestSet<- IP %>% filter(maximum_set==1)

source('~/Documents/UKB Test Space/R/0_transform_for_skew.R')
```
### 8. Deskew
```{r}

#bc_HbA1c_0_imp is already OK

IP<- IP %>% mutate( log_PDA_AoD = trans_log(PDA_AoD),
                    log_pdff =   trans_log(pdff),
                    trans_iron = trans_inverse(iron))

to_clipboard(names(IP))
```
### 9. Liver cT1 categories
```{r}
mid<- IP %>% filter(maximum_set== TRUE)
hist(mid$ct1)
mid$ct1_750<- as.numeric(mid$ct1 >= 750)
mid$ct1_800<- as.numeric(mid$ct1 >= 800)
prop.table(table(mid$ct1_750))
prop.table(table(mid$ct1_800))

#         0         1 
# 0.8404876 0.1595124 


IP$ct1_750 <- as.numeric(IP$ct1 >= 750)
```

### 10. Liver iron categories
```{r}
hist(IP$iron)
skim(IP$iron)

prop.table(table(IP$iron < 1.075 ))
Qs<- quantile(IP$iron, probs = c(0.10, 0.90), na.rm=TRUE) %>% print()
#      10%      90% 
# 1.061159 1.552446 

IP$iron_cat<- case_when(IP$iron >= Qs[2] ~ "2. Iron highest 10%",
                        IP$iron < Qs[1] ~ "1. Iron lowest 10%",
                        is.na(IP$iron) ~ NA_character_, 
                        TRUE ~ "0. Iron middle 80%")
### Checks
table(IP$iron_cat)
boxplot(IP$iron ~ IP$iron_cat)

```
### 11. Reversed CMR

```{r}
IP$aos<-      IP$log_PDA_AoD * -1
IP$red_GFI<-  IP$cmr_GFI * -1
IP$red_LVSV<- IP$cmr_LVSV_i * -1

```


### 12. Orthogonalized Liver (Supp Table 4 first part)
```{r}

cmat<-        IP %>% 
              filter(maximum_set) %>% .[,c("f.eid", "trans_iron", "log_pdff", "ct1")] %>% filter(complete.cases(.))
cmat[-1]<- scale(cmat[,-1])

nrow(cmat) # 11452

pc1<-         psych::principal(cmat[,-1], nfactors = 3); pc1

scores<-      pc1$scores %>% data.frame() %>% 
                rename(pc_iron= RC2,
                       pc_pdff= RC1, 
                       pc_ct1=  RC3) %>%
                mutate(f.eid= cmat$f.eid)

IP<- left_join(IP, scores)

### Checks
plot(IP$log_pdff, IP$pc_pdff);   cor(IP$log_pdff, IP$pc_pdff, use= "pairwise.complete.obs") # 0.9328983
plot(IP$ct1, IP$pc_ct1);         cor(IP$ct1, IP$pc_ct1, use= "pairwise.complete.obs") # 0.9438352
plot(IP$trans_iron, IP$pc_iron); cor(IP$trans_iron, IP$pc_iron, use= "pairwise.complete.obs") # 0.9907269
```

### 13. Orthogonalized CMR (Supp Table 4 second part)
```{r}
cmat<-    IP %>%
  filter(maximum_set) %>% .[, c("f.eid", "red_LVSV", "cmr_LVM_LVEDV", "red_GFI", "aos")] %>% 
  filter(complete.cases(.))
cmat[-1]<- scale(cmat[,-1])

nrow(cmat) # 22798

pc1<-     psych::principal(cmat[,-1], nfactors = 4); pc1
scores<-  pc1$scores %>% data.frame() %>% 
              rename(pc_GFI=   RC4, 
                     pc_aos=   RC2, 
                     pc_LVSV=  RC3, 
                     pc_LVM=   RC1) %>%
              mutate(f.eid= cmat$f.eid)

IP<- left_join(IP, scores)

# Checks
plot(IP$red_LVSV, IP$pc_LVSV);     cor(IP$red_LVSV, IP$pc_LVSV, use= "pairwise.complete.obs") # 0.960558
plot(IP$aos, IP$pc_aos);           cor(IP$aos, IP$pc_aos, use= "pairwise.complete.obs") # 0.9927214
plot(IP$cmr_LVM_LVEDV, IP$pc_LVM); cor(IP$cmr_LVM_LVEDV, IP$pc_LVM, use= "pairwise.complete.obs") #  0.9542762
plot(IP$red_GFI, IP$pc_GFI);       cor(IP$red_GFI, IP$pc_GFI, use= "pairwise.complete.obs") # 0.9426921
```
#--------------------------------------
### Save
```{r}
saveRDS(IP, "../Dev Data 1/IP_1.rds")
dim(IP); get_checksum(IP)
# [1] 502462    269
# [1] 24733293
```

