---
title: "Multi-organ imaging clarifies the connected subclinical pathology of the heart-brain-liver axis in UK Biobank   | Networks - Run 1"

author: "Celeste McCracken"
date:   "25 May 2022"
output: html_notebook
---


### 1. Setup
```{r}
## See setup file for packages and functions
source("00_setup.R")

library(lavaan)

## Output folder
thisFileFolder<- "/Users/celeste/Documents/HBL_Simplified/R/Sept21/"

## Process document (for labels and metadata)
proc<-  read_xlsx("../Proc.xlsx")

```

### 2. Main data input
```{r}
IP<- readRDS("../Dev Data 1/IP_1.rds"); dim(IP); get_checksum(IP)
# [1] 502462    269
# [1] 24733293

SEM<- IP %>% filter(SEM_flag==1) %>% selective_scale(); 
dim(SEM)
#6865  269
```

#------------------

```{r}
set.seed(2021)
reslist<- list()
```

Placed all the variables in together
Leaving out a heart variable if it is not related to the brain variable in pairwise analysis

### 1a.Grey matter volume (Liver --> Heart)

GFI was not significant in pairwise analysis
cT1 is not related to AoD in pairwise analysis

```{r}
modelStringTemplate1a <- 'O_volume_grey_matter_2 ~ a1 * pc_LVSV + a3 * pc_LVM + a4 * pc_aos + b1 * pc_pdff + b2 * pc_ct1 +  m001 * age_2  + m002 * sex + m003 * height_2_imp  + m005 * R01_Diabetes_status_2 + m006 * R02_High_cholesterol_status_2 + m007 * R03_Hypertension_status_2 + m008 * smoker_2 + m009 * trans_mets_2_imp + m010 * alcohol_con_2_imp + m011 * deprivation_Townsend_imp + m012 * educ_imp +  m013 * sbp_2_imp + m014 * obese + m015 * bc_TchoL_0_imp + m016 * bc_HbA1c_0_imp + m017 * bc_RBC_0_imp + m018 * cf_head_size_2_imp + m019 * site +  m026 * cf_pos_X_2_imp + m027 * cf_pos_Y_2_imp + m028 * cf_pos_Z_2_imp + m029 * cf_pos_T_2_imp + m030 * cf_date_2_numeric

pc_LVSV ~ c1 * pc_pdff +  c2 * pc_ct1 + m101 * age_2 + m102 * sex + m103 * height_2_imp + m105 * R01_Diabetes_status_2 + m106 * R02_High_cholesterol_status_2 + m107 * R03_Hypertension_status_2 + m108 * smoker_2 + m109 * trans_mets_2_imp + m110 * alcohol_con_2_imp + m111 * deprivation_Townsend_imp + m112 * educ_imp +  m113 * sbp_2_imp + m114 * obese + m115 * bc_TchoL_0_imp + m116 * bc_HbA1c_0_imp + m117 * bc_RBC_0_imp 

pc_LVM ~ e1 * pc_pdff +  e2 * pc_ct1 +  m301 * age_2 + m302 * sex + m303 * height_2_imp + m305 * R01_Diabetes_status_2 + m306 * R02_High_cholesterol_status_2 + m307 * R03_Hypertension_status_2 + m308 * smoker_2 + m309 * trans_mets_2_imp + m310 * alcohol_con_2_imp + m311 * deprivation_Townsend_imp + m312 * educ_imp +  m313 * sbp_2_imp + m314 * obese + m315 * bc_TchoL_0_imp + m316 * bc_HbA1c_0_imp + m317 * bc_RBC_0_imp 

pc_aos ~ f1 * pc_pdff + m401 * age_2 + m402 * sex + m403 * height_2_imp + m405 * R01_Diabetes_status_2 + m406 * R02_High_cholesterol_status_2 + m407 * R03_Hypertension_status_2 + m408 * smoker_2 + m409 * trans_mets_2_imp + m410 * alcohol_con_2_imp + m411 * deprivation_Townsend_imp + m412 * educ_imp +  m413 * sbp_2_imp + m414 * obese + m415 * bc_TchoL_0_imp + m416 * bc_HbA1c_0_imp + m417 * bc_RBC_0_imp 

indirect_pdff_LVSV := (c1 * a1)
indirect_pdff_LVM :=  (e1 * a3) 
indirect_pdff_aos :=  (f1 * a4)
indirect_pdff_heart := indirect_pdff_LVSV +  indirect_pdff_LVM  + indirect_pdff_aos

indirect_ct1_LVSV :=  (c2 * a1) 
indirect_ct1_LVM := (e2 * a3) 
indirect_ct1_heart := indirect_ct1_LVSV +  indirect_ct1_LVM

total_pdff := indirect_pdff_heart + b1
total_ct1 := indirect_ct1_heart + b2

prop_med_pdff := indirect_pdff_heart / total_pdff
prop_med_ct1 := indirect_ct1_heart / total_ct1
'
```

```{r}
mdl1a<-   sem(modelStringTemplate1a, data= SEM)
res1a<-  parameterestimates(mdl1a, standardized = TRUE, rsquare = TRUE) %>% mutate(ID= "1a", N= mdl1a@SampleStats@ntotal)

out1a<- res1a %>%
   filter(label %like% "a|b|c|d|e|f" | op %in% c(":=", "r2")) %>% mutate(Sig= ifelse(pvalue < 0.05, "*", "")) %>% print() %>%
   to_clipboard()

```
### 1b.Grey matter volume (Heart --> Liver)
```{r}
modelStringTemplate1b <- 'O_volume_grey_matter_2 ~ a1 * pc_LVSV + a3 * pc_LVM + a4 * pc_aos + b1 * pc_pdff + b2 * pc_ct1 +  m001 * age_2  + m002 * sex + m003 * height_2_imp  + m005 * R01_Diabetes_status_2 + m006 * R02_High_cholesterol_status_2 + m007 * R03_Hypertension_status_2 + m008 * smoker_2 + m009 * trans_mets_2_imp + m010 * alcohol_con_2_imp + m011 * deprivation_Townsend_imp + m012 * educ_imp +  m013 * sbp_2_imp + m014 * obese + m015 * bc_TchoL_0_imp + m016 * bc_HbA1c_0_imp + m017 * bc_RBC_0_imp + m018 * cf_head_size_2_imp + m019 * site +  m026 * cf_pos_X_2_imp + m027 * cf_pos_Y_2_imp + m028 * cf_pos_Z_2_imp + m029 * cf_pos_T_2_imp + m030 * cf_date_2_numeric

pc_pdff ~ c1 * pc_LVSV + c2 * pc_GFI + c3 * pc_LVM + c4 * pc_aos + m101 * age_2 + m102 * sex + m103 * height_2_imp + m105 * R01_Diabetes_status_2 + m106 * R02_High_cholesterol_status_2 + m107 * R03_Hypertension_status_2 + m108 * smoker_2 + m109 * trans_mets_2_imp + m110 * alcohol_con_2_imp + m111 * deprivation_Townsend_imp + m112 * educ_imp +  m113 * sbp_2_imp + m114 * obese + m115 * bc_TchoL_0_imp + m116 * bc_HbA1c_0_imp + m117 * bc_RBC_0_imp 

pc_ct1 ~ d1 * pc_LVSV + d2 * pc_GFI + d3 * pc_LVM + d4 * pc_aos +  m301 * age_2 + m302 * sex + m303 * height_2_imp + m305 * R01_Diabetes_status_2 + m306 * R02_High_cholesterol_status_2 + m307 * R03_Hypertension_status_2 + m308 * smoker_2 + m309 * trans_mets_2_imp + m310 * alcohol_con_2_imp + m311 * deprivation_Townsend_imp + m312 * educ_imp +  m313 * sbp_2_imp + m314 * obese + m315 * bc_TchoL_0_imp + m316 * bc_HbA1c_0_imp + m317 * bc_RBC_0_imp 


indirect_LVSV_pdff := (c1 * b1)
indirect_LVSV_ct1  := (d1 * b2)

indirect_LVM_pdff :=  (c3 * b1) 
indirect_LVM_ct1 :=  (d3 * b2)

indirect_GFI_pdff := (c2 * b1)
indirect_GFI_ct1 := (d2 * b2)

indirect_aos_pdff :=  (c4 * b1)
indirect_aos_ct1 := (d4 * b2)

total_LVSV := a1 + indirect_LVSV_pdff + indirect_LVSV_ct1
total_GFI := indirect_GFI_pdff + indirect_GFI_ct1
total_LVM := a3 + indirect_LVM_pdff + indirect_LVM_ct1
total_aos := a4 + indirect_aos_pdff + indirect_aos_ct1

prop_med_LVSV := (indirect_LVSV_pdff + indirect_LVSV_ct1) / total_LVSV
prop_med_GFI := (indirect_GFI_pdff + indirect_GFI_ct1) / total_GFI
prop_med_LVM :=  (indirect_LVM_pdff + indirect_LVM_ct1) / total_LVM
prop_med_aos := (indirect_aos_pdff + indirect_aos_ct1) / total_aos
'
```

```{r}
mdl1b<-   sem(modelStringTemplate1b, data= SEM)
res1b<-  parameterestimates(mdl1b, standardized = TRUE, rsquare = TRUE) %>% mutate(ID= "1b", N= mdl1b@SampleStats@ntotal)

out1b<- res1b %>%
  filter(label %like% "a|b|c|d|e|f" | op %in% c(":=", "r2")) %>% mutate(Sig= ifelse(pvalue < 0.05, "*", "")) %>% print() %>% to_clipboard()

```
### 2a. WMH (Liver --> Heart)
WMH related to all heart and liver in pairwise analysis

```{r}
modelStringTemplate2a <- 'O_volume_WMH_cbrt ~ a1 * pc_LVSV + a2 * pc_GFI + a3 * pc_LVM + a4 * pc_aos + b1 * pc_pdff + b2 * pc_ct1 +  m001 * age_2  + m002 * sex + m003 * height_2_imp  + m005 * R01_Diabetes_status_2 + m006 * R02_High_cholesterol_status_2 + m007 * R03_Hypertension_status_2 + m008 * smoker_2 + m009 * trans_mets_2_imp + m010 * alcohol_con_2_imp + m011 * deprivation_Townsend_imp + m012 * educ_imp +  m013 * sbp_2_imp + m014 * obese + m015 * bc_TchoL_0_imp + m016 * bc_HbA1c_0_imp + m017 * bc_RBC_0_imp + m018 * cf_head_size_2_imp + m019 * site +  m026 * cf_pos_X_2_imp + m027 * cf_pos_Y_2_imp + m028 * cf_pos_Z_2_imp + m029 * cf_pos_T_2_imp + m030 * cf_date_2_numeric

pc_LVSV ~ c1 * pc_pdff +  c2 * ct1 + m101 * age_2 + m102 * sex + m103 * height_2_imp + m105 * R01_Diabetes_status_2 + m106 * R02_High_cholesterol_status_2 + m107 * R03_Hypertension_status_2 + m108 * smoker_2 + m109 * trans_mets_2_imp + m110 * alcohol_con_2_imp + m111 * deprivation_Townsend_imp + m112 * educ_imp +  m113 * sbp_2_imp + m114 * obese + m115 * bc_TchoL_0_imp + m116 * bc_HbA1c_0_imp + m117 * bc_RBC_0_imp 

pc_GFI ~ d1 * pc_pdff +  d2 * pc_ct1 + m201 * age_2 + m202 * sex + m203 * height_2_imp + m205 * R01_Diabetes_status_2 + m206 * R02_High_cholesterol_status_2 + m207 * R03_Hypertension_status_2 + m208 * smoker_2 + m209 * trans_mets_2_imp + m210 * alcohol_con_2_imp + m211 * deprivation_Townsend_imp + m212 * educ_imp +  m213 * sbp_2_imp + m214 * obese + m215 * bc_TchoL_0_imp + m216 * bc_HbA1c_0_imp + m217 * bc_RBC_0_imp 

pc_LVM ~ e1 * pc_pdff +  e2 * pc_ct1 + m301 * age_2 + m302 * sex + m303 * height_2_imp + m305 * R01_Diabetes_status_2 + m306 * R02_High_cholesterol_status_2 + m307 * R03_Hypertension_status_2 + m308 * smoker_2 + m309 * trans_mets_2_imp + m310 * alcohol_con_2_imp + m311 * deprivation_Townsend_imp + m312 * educ_imp +  m313 * sbp_2_imp + m314 * obese + m315 * bc_TchoL_0_imp + m316 * bc_HbA1c_0_imp + m317 * bc_RBC_0_imp 

pc_aos ~ f1 * pc_pdff + m401 * age_2 + m402 * sex + m403 * height_2_imp + m405 * R01_Diabetes_status_2 + m406 * R02_High_cholesterol_status_2 + m407 * R03_Hypertension_status_2 + m408 * smoker_2 + m409 * trans_mets_2_imp + m410 * alcohol_con_2_imp + m411 * deprivation_Townsend_imp + m412 * educ_imp +  m413 * sbp_2_imp + m414 * obese + m415 * bc_TchoL_0_imp + m416 * bc_HbA1c_0_imp + m417 * bc_RBC_0_imp 


indirect_pdff_LVSV := (c1 * a1)
indirect_pdff_GFI  := (d1 * a2) 
indirect_pdff_LVM :=  (e1 * a3) 
indirect_pdff_aos :=  (f1 * a4)
indirect_pdff_heart := indirect_pdff_LVSV + indirect_pdff_GFI + indirect_pdff_LVM  + indirect_pdff_aos

indirect_ct1_LVSV :=  (c2 * a1) 
indirect_ct1_GFI := (d2 * a2) 
indirect_ct1_LVM := (e2 * a3) 
indirect_ct1_heart := indirect_ct1_LVSV + indirect_ct1_GFI + indirect_ct1_LVM

total_pdff := indirect_pdff_heart + b1
total_ct1 := indirect_ct1_heart + b2

prop_med_pdff := indirect_pdff_heart / total_pdff
prop_med_ct1 := indirect_ct1_heart / total_ct1

'
```

```{r}
mdl2a<- sem(modelStringTemplate2a, data= SEM)
res2a<-   parameterestimates(mdl2a, standardized = TRUE, rsquare= TRUE) %>% mutate(ID= "2a", N= mdl2a@SampleStats@ntotal)

out2a<- res2a %>%
    filter(label %like% "a|b|c|d|e|f" | op %in% c(":=", "r2")) %>% mutate(Sig= ifelse(pvalue < 0.05, "*", "")) %>% print() %>% to_clipboard()

```
### 2b. WMH (Heart --> Liver)

```{r}
modelStringTemplate2b <- 'O_volume_WMH_cbrt ~ a1 * pc_LVSV  + a2 * pc_GFI + a3 * pc_LVM + a4 * pc_aos + b1 * pc_pdff + b2 * pc_ct1 +  m001 * age_2  + m002 * sex + m003 * height_2_imp  + m005 * R01_Diabetes_status_2 + m006 * R02_High_cholesterol_status_2 + m007 * R03_Hypertension_status_2 + m008 * smoker_2 + m009 * trans_mets_2_imp + m010 * alcohol_con_2_imp + m011 * deprivation_Townsend_imp + m012 * educ_imp +  m013 * sbp_2_imp + m014 * obese + m015 * bc_TchoL_0_imp + m016 * bc_HbA1c_0_imp + m017 * bc_RBC_0_imp + m018 * cf_head_size_2_imp + m019 * site +  m026 * cf_pos_X_2_imp + m027 * cf_pos_Y_2_imp + m028 * cf_pos_Z_2_imp + m029 * cf_pos_T_2_imp + m030 * cf_date_2_numeric

pc_pdff ~ c1 * pc_LVSV + c2 * pc_GFI + c3 * pc_LVM + c4 * pc_aos + m101 * age_2 + m102 * sex + m103 * height_2_imp + m105 * R01_Diabetes_status_2 + m106 * R02_High_cholesterol_status_2 + m107 * R03_Hypertension_status_2 + m108 * smoker_2 + m109 * trans_mets_2_imp + m110 * alcohol_con_2_imp + m111 * deprivation_Townsend_imp + m112 * educ_imp +  m113 * sbp_2_imp + m114 * obese + m115 * bc_TchoL_0_imp + m116 * bc_HbA1c_0_imp + m117 * bc_RBC_0_imp 

pc_ct1 ~ d1 * pc_LVSV + d2 * pc_GFI + d3 * pc_LVM + d4 * pc_aos +  m301 * age_2 + m302 * sex + m303 * height_2_imp + m305 * R01_Diabetes_status_2 + m306 * R02_High_cholesterol_status_2 + m307 * R03_Hypertension_status_2 + m308 * smoker_2 + m309 * trans_mets_2_imp + m310 * alcohol_con_2_imp + m311 * deprivation_Townsend_imp + m312 * educ_imp +  m313 * sbp_2_imp + m314 * obese + m315 * bc_TchoL_0_imp + m316 * bc_HbA1c_0_imp + m317 * bc_RBC_0_imp 


indirect_LVSV_pdff := (c1 * b1)
indirect_LVSV_ct1  := (d1 * b2)

indirect_GFI_pdff := (c2 * b1)
indirect_GFI_ct1 := (d2 * b2)

indirect_LVM_pdff :=  (c3 * b1) 
indirect_LVM_ct1 :=  (d3 * b2)

indirect_aos_pdff :=  (c4 * b1)
indirect_aos_ct1 := (d4 * b2)

total_LVSV := a1 + indirect_LVSV_pdff + indirect_LVSV_ct1
total_GFI := a2 + indirect_GFI_pdff + indirect_GFI_ct1
total_LVM := a3 + indirect_LVM_pdff + indirect_LVM_ct1
total_aos := a4 + indirect_aos_pdff + indirect_aos_ct1

prop_med_LVSV := (indirect_LVSV_pdff + indirect_LVSV_ct1) / total_LVSV
prop_med_GFI := (indirect_GFI_pdff + indirect_GFI_ct1) / total_GFI
prop_med_LVM :=  (indirect_LVM_pdff + indirect_LVM_ct1) / total_LVM
prop_med_aos := (indirect_aos_pdff + indirect_aos_ct1) / total_aos
'
```

```{r}
mdl2b<- sem(modelStringTemplate2b, data= SEM)
res2b<-   parameterestimates(mdl2b, standardized = TRUE, rsquare= TRUE) %>% mutate(ID= "2b", N= mdl2b@SampleStats@ntotal)

out2b<- res2b %>%
    filter(label %like% "a|b|c|d|e|f" | op %in% c(":=", "r2")) %>% mutate(Sig= ifelse(pvalue < 0.05, "*", "")) %>% print() %>% to_clipboard()
```


### 3a. ICVF (Liver --> Heart)
LVSV not related to ICVF in pairwise analyses
```{r}
modelStringTemplate3a <- 'ICVF ~  a2 * pc_GFI +  a3 * pc_LVM + a4 * pc_aos + b1 * pc_pdff + b2 * pc_ct1 +  m001 * age_2  + m002 * sex + m003 * height_2_imp  + m005 * R01_Diabetes_status_2 + m006 * R02_High_cholesterol_status_2 + m007 * R03_Hypertension_status_2 + m008 * smoker_2 + m009 * trans_mets_2_imp + m010 * alcohol_con_2_imp + m011 * deprivation_Townsend_imp + m012 * educ_imp +  m013 * sbp_2_imp + m014 * obese + m015 * bc_TchoL_0_imp + m016 * bc_HbA1c_0_imp + m017 * bc_RBC_0_imp + m018 * cf_head_size_2_imp + m019 * site +  m026 * cf_pos_X_2_imp + m027 * cf_pos_Y_2_imp + m028 * cf_pos_Z_2_imp + m029 * cf_pos_T_2_imp + m030 * cf_date_2_numeric


pc_GFI ~ d1 * pc_pdff +  d2 * pc_ct1 + m201 * age_2  + m202 * sex + m203 * height_2_imp + m205 * R01_Diabetes_status_2 + m206 * R02_High_cholesterol_status_2 + m207 * R03_Hypertension_status_2 + m208 * smoker_2 + m209 * trans_mets_2_imp + m210 * alcohol_con_2_imp + m211 * deprivation_Townsend_imp + m212 * educ_imp +  m213 * sbp_2_imp + m214 * obese + m215 * bc_TchoL_0_imp + m216 * bc_HbA1c_0_imp + m217 * bc_RBC_0_imp 

pc_LVM ~ e1 * pc_pdff +  e2 * pc_ct1 + m301 * age_2 + m302 * sex + m303 * height_2_imp + m305 * R01_Diabetes_status_2 + m306 * R02_High_cholesterol_status_2 + m307 * R03_Hypertension_status_2 + m308 * smoker_2 + m309 * trans_mets_2_imp + m310 * alcohol_con_2_imp + m311 * deprivation_Townsend_imp + m312 * educ_imp +  m313 * sbp_2_imp + m314 * obese + m315 * bc_TchoL_0_imp + m316 * bc_HbA1c_0_imp + m317 * bc_RBC_0_imp 

pc_aos ~ f1 * pc_pdff + m401 * age_2 + m402 * sex + m403 * height_2_imp + m405 * R01_Diabetes_status_2 + m406 * R02_High_cholesterol_status_2 + m407 * R03_Hypertension_status_2 + m408 * smoker_2 + m409 * trans_mets_2_imp + m410 * alcohol_con_2_imp + m411 * deprivation_Townsend_imp + m412 * educ_imp +  m413 * sbp_2_imp + m414 * obese + m415 * bc_TchoL_0_imp + m416 * bc_HbA1c_0_imp + m417 * bc_RBC_0_imp 


indirect_pdff_GFI  := (d1 * a2) 
indirect_pdff_LVM :=  (e1 * a3) 
indirect_pdff_aos :=  (f1 * a4)
indirect_pdff_heart :=   indirect_pdff_GFI + indirect_pdff_LVM  + indirect_pdff_aos


indirect_ct1_GFI := (d2 * a2) 
indirect_ct1_LVM := (e2 * a3) 
indirect_ct1_heart :=  indirect_ct1_GFI + indirect_ct1_LVM

total_pdff := indirect_pdff_heart + b1
total_ct1 := indirect_ct1_heart + b2

prop_med_pdff := indirect_pdff_heart / total_pdff
prop_med_ct1 := indirect_ct1_heart / total_ct1

'
```

```{r}
mdl3a<- sem(modelStringTemplate3a, data= SEM)
res3a<-   parameterestimates(mdl3a, standardized = TRUE, rsquare= TRUE) %>% mutate(ID= "3a", N= mdl3a@SampleStats@ntotal)
out3a<- res3a %>%
    filter(label %like% "a|b|c|d|e|f" | op %in% c(":=", "r2")) %>% mutate(Sig= ifelse(pvalue < 0.05, "*", "")) %>% print() %>% to_clipboard()

```

### 3b. ICVF (Heart --> Liver)
```{r}
modelStringTemplate3b <- 'ICVF ~  + a2 * pc_GFI + a3 * pc_LVM + a4 * pc_aos + b1 * pc_pdff + b2 * pc_ct1 +  m001 * age_2  + m002 * sex + m003 * height_2_imp  + m005 * R01_Diabetes_status_2 + m006 * R02_High_cholesterol_status_2 + m007 * R03_Hypertension_status_2 + m008 * smoker_2 + m009 * trans_mets_2_imp + m010 * alcohol_con_2_imp + m011 * deprivation_Townsend_imp + m012 * educ_imp +  m013 * sbp_2_imp + m014 * obese + m015 * bc_TchoL_0_imp + m016 * bc_HbA1c_0_imp + m017 * bc_RBC_0_imp + m018 * cf_head_size_2_imp + m019 * site +  m026 * cf_pos_X_2_imp + m027 * cf_pos_Y_2_imp + m028 * cf_pos_Z_2_imp + m029 * cf_pos_T_2_imp + m030 * cf_date_2_numeric

pc_pdff ~ c1 * pc_LVSV + c2 * pc_GFI + c3 * pc_LVM + c4 * pc_aos + m101 * age_2 + m102 * sex + m103 * height_2_imp + m105 * R01_Diabetes_status_2 + m106 * R02_High_cholesterol_status_2 + m107 * R03_Hypertension_status_2 + m108 * smoker_2 + m109 * trans_mets_2_imp + m110 * alcohol_con_2_imp + m111 * deprivation_Townsend_imp + m112 * educ_imp +  m113 * sbp_2_imp + m114 * obese + m115 * bc_TchoL_0_imp + m116 * bc_HbA1c_0_imp + m117 * bc_RBC_0_imp 

pc_ct1 ~ d1 * pc_LVSV + d2 * pc_GFI + d3 * pc_LVM + d4 * pc_aos +  m301 * age_2 + m302 * sex + m303 * height_2_imp + m305 * R01_Diabetes_status_2 + m306 * R02_High_cholesterol_status_2 + m307 * R03_Hypertension_status_2 + m308 * smoker_2 + m309 * trans_mets_2_imp + m310 * alcohol_con_2_imp + m311 * deprivation_Townsend_imp + m312 * educ_imp +  m313 * sbp_2_imp + m314 * obese + m315 * bc_TchoL_0_imp + m316 * bc_HbA1c_0_imp + m317 * bc_RBC_0_imp 


indirect_LVSV_pdff := (c1 * b1)
indirect_LVSV_ct1  := (d1 * b2)

indirect_GFI_pdff := (c2 * b1)
indirect_GFI_ct1 := (d2 * b2)

indirect_LVM_pdff :=  (c3 * b1) 
indirect_LVM_ct1 :=  (d3 * b2)

indirect_aos_pdff :=  (c4 * b1)
indirect_aos_ct1 := (d4 * b2)

total_LVSV := indirect_LVSV_pdff + indirect_LVSV_ct1
total_GFI := a2 + indirect_GFI_pdff + indirect_GFI_ct1
total_LVM := a3 + indirect_LVM_pdff + indirect_LVM_ct1
total_aos := a4 + indirect_aos_pdff + indirect_aos_ct1

prop_med_LVSV := (indirect_LVSV_pdff + indirect_LVSV_ct1) / total_LVSV
prop_med_GFI := (indirect_GFI_pdff + indirect_GFI_ct1) / total_GFI
prop_med_LVM :=  (indirect_LVM_pdff + indirect_LVM_ct1) / total_LVM
prop_med_aos := (indirect_aos_pdff + indirect_aos_ct1) / total_aos
'
```

```{r}
mdl3b<- sem(modelStringTemplate3b, data= SEM)
res3b<-   parameterestimates(mdl3b, standardized = TRUE, rsquare= TRUE) %>% mutate(ID= "3b", N= mdl3b@SampleStats@ntotal)
out3b<- res3b %>%
    filter(label %like% "a|b|c|d|e|f" | op %in% c(":=", "r2")) %>% mutate(Sig= ifelse(pvalue < 0.05, "*", "")) %>% print() %>% to_clipboard()
```

### 4a. ISOVF (Liver --> Heart)
LVSV is not related to ISOVF in pairwise analyses
```{r}
modelStringTemplate4a <- 'ISOVF ~ a2 * pc_GFI +  a3 * pc_LVM + a4 * pc_aos + b1 * pc_pdff + b2 * pc_ct1 +  m001 * age_2  + m002 * sex + m003 * height_2_imp  + m005 * R01_Diabetes_status_2 + m006 * R02_High_cholesterol_status_2 + m007 * R03_Hypertension_status_2 + m008 * smoker_2 + m009 * trans_mets_2_imp + m010 * alcohol_con_2_imp + m011 * deprivation_Townsend_imp + m012 * educ_imp +  m013 * sbp_2_imp + m014 * obese + m015 * bc_TchoL_0_imp + m016 * bc_HbA1c_0_imp + m017 * bc_RBC_0_imp + m018 * cf_head_size_2_imp + m019 * site +  m026 * cf_pos_X_2_imp + m027 * cf_pos_Y_2_imp + m028 * cf_pos_Z_2_imp + m029 * cf_pos_T_2_imp + m030 * cf_date_2_numeric

pc_GFI ~ d1 * pc_pdff +  d2 * pc_ct1 + m201 * age_2  + m202 * sex + m203 * height_2_imp + m205 * R01_Diabetes_status_2 + m206 * R02_High_cholesterol_status_2 + m207 * R03_Hypertension_status_2 + m208 * smoker_2 + m209 * trans_mets_2_imp + m210 * alcohol_con_2_imp + m211 * deprivation_Townsend_imp + m212 * educ_imp +  m213 * sbp_2_imp + m214 * obese + m215 * bc_TchoL_0_imp + m216 * bc_HbA1c_0_imp + m217 * bc_RBC_0_imp 

pc_LVM ~ e1 * pc_pdff +  e2 * pc_ct1 + m301 * age_2 + m302 * sex + m303 * height_2_imp + m305 * R01_Diabetes_status_2 + m306 * R02_High_cholesterol_status_2 + m307 * R03_Hypertension_status_2 + m308 * smoker_2 + m309 * trans_mets_2_imp + m310 * alcohol_con_2_imp + m311 * deprivation_Townsend_imp + m312 * educ_imp +  m313 * sbp_2_imp + m314 * obese + m315 * bc_TchoL_0_imp + m316 * bc_HbA1c_0_imp + m317 * bc_RBC_0_imp 

pc_aos ~ f1 * pc_pdff + m401 * age_2 + m402 * sex + m403 * height_2_imp + m405 * R01_Diabetes_status_2 + m406 * R02_High_cholesterol_status_2 + m407 * R03_Hypertension_status_2 + m408 * smoker_2 + m409 * trans_mets_2_imp + m410 * alcohol_con_2_imp + m411 * deprivation_Townsend_imp + m412 * educ_imp +  m413 * sbp_2_imp + m414 * obese + m415 * bc_TchoL_0_imp + m416 * bc_HbA1c_0_imp + m417 * bc_RBC_0_imp 



indirect_pdff_GFI  := (d1 * a2) 
indirect_pdff_LVM :=  (e1 * a3) 
indirect_pdff_aos :=  (f1 * a4)
indirect_pdff_heart :=  indirect_pdff_GFI + indirect_pdff_LVM  + indirect_pdff_aos

 
indirect_ct1_GFI := (d2 * a2) 
indirect_ct1_LVM := (e2 * a3) 
indirect_ct1_heart := indirect_ct1_GFI + indirect_ct1_LVM

total_pdff := indirect_pdff_heart + b1
total_ct1 := indirect_ct1_heart + b2

prop_med_pdff := indirect_pdff_heart / total_pdff
prop_med_ct1 := indirect_ct1_heart / total_ct1

'
```

```{r}
mdl4a<- sem(modelStringTemplate4a, data= SEM)
res4a<-   parameterestimates(mdl4a, standardized = TRUE, rsquare= TRUE) %>% mutate(ID= "4a", N= mdl4a@SampleStats@ntotal)
out4a<- res4a %>%
    filter(label %like% "a|b|c|d|e|f" | op %in% c(":=", "r2")) %>% mutate(Sig= ifelse(pvalue < 0.05, "*", "")) %>% print() %>% to_clipboard()

```

### 4b. ISOVF (Heart --> Liver)
```{r}
modelStringTemplate4b <- 'ISOVF ~  + a2 * pc_GFI + a3 * pc_LVM + a4 * pc_aos + b1 * pc_pdff + b2 * pc_ct1 +  m001 * age_2  + m002 * sex + m003 * height_2_imp  + m005 * R01_Diabetes_status_2 + m006 * R02_High_cholesterol_status_2 + m007 * R03_Hypertension_status_2 + m008 * smoker_2 + m009 * trans_mets_2_imp + m010 * alcohol_con_2_imp + m011 * deprivation_Townsend_imp + m012 * educ_imp +  m013 * sbp_2_imp + m014 * obese + m015 * bc_TchoL_0_imp + m016 * bc_HbA1c_0_imp + m017 * bc_RBC_0_imp + m018 * cf_head_size_2_imp + m019 * site +  m026 * cf_pos_X_2_imp + m027 * cf_pos_Y_2_imp + m028 * cf_pos_Z_2_imp + m029 * cf_pos_T_2_imp + m030 * cf_date_2_numeric

pc_pdff ~ c1 * pc_LVSV + c2 * pc_GFI + c3 * pc_LVM + c4 * pc_aos + m101 * age_2 + m102 * sex + m103 * height_2_imp + m105 * R01_Diabetes_status_2 + m106 * R02_High_cholesterol_status_2 + m107 * R03_Hypertension_status_2 + m108 * smoker_2 + m109 * trans_mets_2_imp + m110 * alcohol_con_2_imp + m111 * deprivation_Townsend_imp + m112 * educ_imp +  m113 * sbp_2_imp + m114 * obese + m115 * bc_TchoL_0_imp + m116 * bc_HbA1c_0_imp + m117 * bc_RBC_0_imp 

pc_ct1 ~ d1 * pc_LVSV + d2 * pc_GFI + d3 * pc_LVM + d4 * pc_aos +  m301 * age_2 + m302 * sex + m303 * height_2_imp + m305 * R01_Diabetes_status_2 + m306 * R02_High_cholesterol_status_2 + m307 * R03_Hypertension_status_2 + m308 * smoker_2 + m309 * trans_mets_2_imp + m310 * alcohol_con_2_imp + m311 * deprivation_Townsend_imp + m312 * educ_imp +  m313 * sbp_2_imp + m314 * obese + m315 * bc_TchoL_0_imp + m316 * bc_HbA1c_0_imp + m317 * bc_RBC_0_imp 


indirect_LVSV_pdff := (c1 * b1)
indirect_LVSV_ct1  := (d1 * b2)

indirect_GFI_pdff := (c2 * b1)
indirect_GFI_ct1 := (d2 * b2)

indirect_LVM_pdff :=  (c3 * b1) 
indirect_LVM_ct1 :=  (d3 * b2)

indirect_aos_pdff :=  (c4 * b1)
indirect_aos_ct1 := (d4 * b2)

total_LVSV := indirect_LVSV_pdff + indirect_LVSV_ct1
total_GFI := a2 + indirect_GFI_pdff + indirect_GFI_ct1
total_LVM := a3 + indirect_LVM_pdff + indirect_LVM_ct1
total_aos := a4 + indirect_aos_pdff + indirect_aos_ct1

prop_med_LVSV := (indirect_LVSV_pdff + indirect_LVSV_ct1) / total_LVSV
prop_med_GFI := (indirect_GFI_pdff + indirect_GFI_ct1) / total_GFI
prop_med_LVM :=  (indirect_LVM_pdff + indirect_LVM_ct1) / total_LVM
prop_med_aos := (indirect_aos_pdff + indirect_aos_ct1) / total_aos
'
```

```{r}
mdl4b<- sem(modelStringTemplate4b, data= SEM)
res4b<-   parameterestimates(mdl4b, standardized = TRUE, rsquare= TRUE) %>% mutate(ID= "4b", N= mdl4b@SampleStats@ntotal)
out4b<- res4b %>%
    filter(label %like% "a|b|c|d|e|f" | op %in% c(":=", "r2")) %>% mutate(Sig= ifelse(pvalue < 0.05, "*", "")) %>% print() %>% to_clipboard()
```


### Output
```{r}
models<- list(mdl1a, mdl1b, mdl2a, mdl2b, mdl3a, mdl3b, mdl4a, mdl4b)

saveRDS(models, "Networks_HBL_run1.rds")

outputs<- bind_rows(out1a, out1b, out2a, out2b, out3a, out3b, out4a, out4b)
write_xlsx(outputs, "Networks_HBL_run1.xlsx")
```





